Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2013-12-15 ms.tex
more introduction

\cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum.

@@

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|. \verb|i100| has angular resolution of $6.1'$. %list other
%important characteristics of i100 e.g. that it has been zodi-corrected
% and relies on dirbe on scales larger than ???

@@

\subsection{Comparison to Planck Collaboration Dust Map}

>>>>

\cite{planckdust} has recently conducted a study modeling
\PLANCK~353 GHz, 545 GHz, 857 GHz and IRAS 100$\mu$m emission with a single
MBB spectrum. Here we investigate the FDS99 two-component dust emission model 
as an alernative model for the dust SED composed of \PLANCK~and \IRAS~data. In
doing so, we obtain $6.1'$ maps of dust temperature and optical depth. Because
we are using a model that has been validated using FIRAS data down to sub-mm
wavelengths, this model should be useful in constructing predictions of dust
emission over a very broad range of wavelengths. This includes low frequencies,
which \cite{planckdust} admit their model does not adequately fit, and also
data near the peak of the dust SED, for example Akari. We also anticipate 
the optical depth map we derive will be useful as a comparison for extinction
estimates based directly upon optical/NIR observations of stars.

%would be nice if i had a citation here for Eddie/Greg pan-starrs dust stuff

@@

To incorporate information about the dust emission on the Wien side of its 
spectrum, we make use of 100$\mu$m data. In particular, we use the SFD 
reprocessing of IRAS 100$\mu$m, which we will refer to as \verb|i100|, and at 
times by frequency as 3000 GHz. \verb|i100| has angular resolution of $6.1'$. 
%list other %important characteristics of i100 e.g. that it has been 
%zodi-corrected and relies on dirbe on scales larger than ???

@@

\subsection{Comparison to Planck Collaboration Dust Map}
%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
